TacticToe: Learning to Prove with Tactics

### 2018-03-27 tactictoe_jv.tex
minor

The MCTS evaluation, despite relying on the largest amount of collected data,
does not provide a significant improvement over a strategy relying on no
evaluation. The minor improvement seen in the table is most likely due to some
variability in our experiments.
The main reason is that our predictor learning abilities is
limited and we are using the provability of lists of goals for evaluation. A
more accurate evaluation could be based on an estimation of the length of the
proof required to close a list of goals.

>>>>

The MCTS evaluation, despite relying on the largest amount of collected data,
does not provide a significant improvement over a strategy relying on no
evaluation. The main reason is that our predictor learning abilities is
limited and we are using an estimate of the provability of lists of goals for 
evaluation. A more accurate evaluation could be based on an estimation of the 
length of the proof required to close a list of goals.
